---
title: "Initial_DataAnalysis"
output: html_document
---

# Loading packages and reading the data

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, error = TRUE, cache = TRUE)
library(knitr)
library(readxl)
library(tidyverse)

# Loading the data
data <- read.csv('analysisTable_zScore_EQ.txt')
```

# Inspecting the data

```{r}
head(data)
summary(data)
```

No cases of Autism Specturm Disorder. However, max score of LSAS\_overall is 83 which indicates Social Anxiety. 

```{r}
unique(data[data$LSAS_overall > 60, 'ID']) # Persons with Social Anxiety 
```


# Participants

```{r}
unique_subj <- unlist(unique(data[1]), use.names = FALSE)
paste0('There are ', length(unique_subj), ' subjects.')

cnt_obs_subj <- numeric()
for (i in 1:length(unique_subj)) {
  cnt_obs_subj[i] <- sum(data[1] == unique_subj[i])
}
unique(cnt_obs_subj) # Every subject has 7725 measures
```

# Trials

```{r}
unique_trial <- sort(unlist(unique(data[2]), use.names = FALSE))
paste0('There are ', length(unique_trial), ' trials.') 

cnt_trials <- numeric()
for (i in 1:length(unique_trial)) {
  cnt_trials[i] <- sum(data[2] == unique_trial[i])
}
unique(cnt_trials) # There are 5025, 5100, 4950, 4875 meaures for trials

```

Every participant misses one trial.


# Means

```{r, include= FALSE}
mean(data$Age)
mean(data$AQ_overall)
mean(data$LSAS_overall)
mean(data$EQ_overall)
mean(data$baselineCorrected_EMG_Cor_zScore, na.rm = TRUE) # With NA's removed
mean(data$baselineCorrected_EMG_Zyg_zScore, na.rm = TRUE) # With NA's removed
mean(data$baselineCorrected_SC_zScore, na.rm = TRUE) # With NA's removed
mean(data$baselineCorrected_SKT_zScore, na.rm = TRUE) # With NA's removed
mean(data$baselineCorrected_DIA_zScore, na.rm = TRUE) # With NA's removed

```


```{r}
# Group by Slice
data_tib <- as_tibble(data)

by_Slice <- data_tib %>% group_by(Slice)

# Means of signals per slice
sum_slice <- by_Slice %>% summarise(Mean_Cor = mean(baselineCorrected_EMG_Cor_zScore, na.rm = TRUE), Mean_Zyg = mean(baselineCorrected_EMG_Zyg_zScore, na.rm = TRUE), Mean_SC = mean(baselineCorrected_SC_zScore, na.rm = TRUE), Mean_SKT = mean(baselineCorrected_SKT_zScore, na.rm = TRUE), Mean_DIA = mean(baselineCorrected_DIA_zScore, na.rm = TRUE))

sum_slice

```


```{r}
# Group by Slice and Labeled emotion
data_tib <- as_tibble(data)

by_SliceEMO <- data_tib %>% group_by(Slice, label_string)

# Means of signals per slice per labeled emotion
sum_sliceEMO <- by_SliceEMO %>% summarise(Mean_Cor = mean(baselineCorrected_EMG_Cor_zScore, na.rm = TRUE), Mean_Zyg = mean(baselineCorrected_EMG_Zyg_zScore, na.rm = TRUE), Mean_SC = mean(baselineCorrected_SC_zScore, na.rm = TRUE), Mean_SKT = mean(baselineCorrected_SKT_zScore, na.rm = TRUE), Mean_DIA = mean(baselineCorrected_DIA_zScore, na.rm = TRUE))

sum_sliceEMO

```



```{r}
# Group by Slice and ID
by_SliceID <- data_tib %>% group_by(Slice, ID)

# Means of signal per ID per slice
sum_sliceID <- by_SliceID %>% summarise(Mean_Cor = mean(baselineCorrected_EMG_Cor_zScore, na.rm = TRUE), Mean_Zyg = mean(baselineCorrected_EMG_Zyg_zScore, na.rm = TRUE), Mean_SC = mean(baselineCorrected_SC_zScore, na.rm = TRUE), Mean_SKT = mean(baselineCorrected_SKT_zScore, na.rm = TRUE), Mean_DIA = mean(baselineCorrected_DIA_zScore, na.rm = TRUE))

sum_sliceID

```


# Descriptives and plots

```{r, include=FALSE}
# Age
boxplot(data$Age)

# Gender
plot(data$Gender)

# Handedness
plot(data$Handedness)
unique(data[c(data$Handedness == 'NaN'), 'ID']) # ID with missing Handedness

# mean EMG Corrugator
xstim <- c(1:40)
xblank <- c(41:75)
mean_cor_stim <- sum_slice$Mean_Cor[1:40]
mean_cor_blank <- sum_slice$Mean_Cor[41:75]
reg_stim <- lm(mean_cor_stim ~ xstim)
reg_blank <- lm(mean_cor_blank ~ xblank)

plot(sum_slice$Mean_Cor, type = 'l', xlab = 'Slices', ylab = 'Mean EMG_Cor')
abline(v = 40, col = 'red')
lines(reg_stim$fitted.values, col = 'blue')
lines(x = c(40:74), reg_blank$fitted.values, col = 'green')

# mean EMG Zygomaticus
xstim <- c(1:40)
xblank <- c(41:75)
mean_zyg_stim <- sum_slice$Mean_Zyg[1:40]
mean_zyg_blank <- sum_slice$Mean_Zyg[41:75]
reg_stim <- lm(mean_zyg_stim ~ xstim)
reg_blank <- lm(mean_zyg_blank ~ xblank)

plot(sum_slice$Mean_Zyg, type = 'l', xlab = 'Slices', ylab = 'Mean EMG_Zyg')
abline(v = 40, col = 'red')
lines(reg_stim$fitted.values, col = 'blue')
lines(x = c(40:74), reg_blank$fitted.values, col = 'green')

# mean Skin Conductance
xstim <- c(1:40)
xblank <- c(41:75)
mean_sc_stim <- sum_slice$Mean_SC[1:40]
mean_sc_blank <- sum_slice$Mean_SC[41:75]
reg_stim <- lm(mean_sc_stim ~ xstim)
reg_blank <- lm(mean_sc_blank ~ xblank)

plot(sum_slice$Mean_SC, type = 'l', xlab = 'Slices', ylab = 'Mean SC')
abline(v = 40, col = 'red')
lines(reg_stim$fitted.values, col = 'blue')
lines(x = c(40:74), reg_blank$fitted.values, col = 'green')

# mean Skin Temperature
xstim <- c(1:40)
xblank <- c(41:75)
mean_skt_stim <- sum_slice$Mean_SKT[1:40]
mean_skt_blank <- sum_slice$Mean_SKT[41:75]
reg_stim <- lm(mean_skt_stim ~ xstim)
reg_blank <- lm(mean_skt_blank ~ xblank)

plot(sum_slice$Mean_SKT, type = 'l', xlab = 'Slices', ylab = 'Mean SKT')
abline(v = 40, col = 'red')
lines(reg_stim$fitted.values, col = 'blue')
lines(x = c(40:74), reg_blank$fitted.values, col = 'green')

# mean Pupil Diameter
xstim <- c(1:40)
xblank <- c(41:75)
mean_dia_stim <- sum_slice$Mean_DIA[1:40]
mean_dia_blank <- sum_slice$Mean_DIA[41:75]
reg_stim <- lm(mean_dia_stim ~ xstim)
reg_blank <- lm(mean_dia_blank ~ xblank)

plot(sum_slice$Mean_DIA, type = 'l', xlab = 'Slices', ylab = 'Mean DIA')
abline(v = 40, col = 'red')
lines(reg_stim$fitted.values, col = 'blue')
lines(x = c(40:74), reg_blank$fitted.values, col = 'green')
```




```{r}
# Plot mean signal score per emotion

# EMG Cor
plot(sum_sliceEMO[sum_sliceEMO$label_string == 'angry', 'Mean_Cor'][[1]], type = 'l', xlab = 'Slices', ylab = 'Mean EMG_Cor', ylim = range(c(-0.12, 0.12)))
abline(v = 40, col = 'red')
lines(sum_sliceEMO[sum_sliceEMO$label_string == 'sad', 'Mean_Cor'][[1]], col = 'blue')
lines(sum_sliceEMO[sum_sliceEMO$label_string == 'happy', 'Mean_Cor'][[1]], col = 'green')
lines(sum_sliceEMO[sum_sliceEMO$label_string == 'neutral', 'Mean_Cor'][[1]], col = 'orange')
lines(sum_sliceEMO[sum_sliceEMO$label_string == 'scared', 'Mean_Cor'][[1]], col = 'purple')
legend('topright',inset = 0.02,legend = c('angry', 'sad', 'happy', 'neutral', 'scared'),col = c('black', 'blue', 'green', 'orange', 'purple'), cex = 0.60, lty = 1)

# EMG Zyg
plot(sum_sliceEMO[sum_sliceEMO$label_string == 'angry', 'Mean_Zyg'][[1]], type = 'l', xlab = 'Slices', ylab = 'Mean EMG_Zyg', ylim = range(c(-0.1, 0.15)))
abline(v = 40, col = 'red')
lines(sum_sliceEMO[sum_sliceEMO$label_string == 'sad', 'Mean_Zyg'][[1]], col = 'blue')
lines(sum_sliceEMO[sum_sliceEMO$label_string == 'happy', 'Mean_Zyg'][[1]], col = 'green')
lines(sum_sliceEMO[sum_sliceEMO$label_string == 'neutral', 'Mean_Zyg'][[1]], col = 'orange')
lines(sum_sliceEMO[sum_sliceEMO$label_string == 'scared', 'Mean_Zyg'][[1]], col = 'purple')
legend('topleft',inset = 0.02,legend = c('angry', 'sad', 'happy', 'neutral', 'scared'),col = c('black', 'blue', 'green', 'orange', 'purple'), cex = 0.50, lty = 1)

# SC
plot(sum_sliceEMO[sum_sliceEMO$label_string == 'angry', 'Mean_SC'][[1]], type = 'l', xlab = 'Slices', ylab = 'Mean SC', ylim = range(c(-0.15, 0.15)))
abline(v = 40, col = 'red')
lines(sum_sliceEMO[sum_sliceEMO$label_string == 'sad', 'Mean_SC'][[1]], col = 'blue')
lines(sum_sliceEMO[sum_sliceEMO$label_string == 'happy', 'Mean_SC'][[1]], col = 'green')
lines(sum_sliceEMO[sum_sliceEMO$label_string == 'neutral', 'Mean_SC'][[1]], col = 'orange')
lines(sum_sliceEMO[sum_sliceEMO$label_string == 'scared', 'Mean_SC'][[1]], col = 'purple')
legend('topright',inset = 0.02,legend = c('angry', 'sad', 'happy', 'neutral', 'scared'),col = c('black', 'blue', 'green', 'orange', 'purple'), cex = 0.60, lty = 1)

# SKT
plot(sum_sliceEMO[sum_sliceEMO$label_string == 'angry', 'Mean_SKT'][[1]], type = 'l', xlab = 'Slices', ylab = 'Mean SKT', ylim = range(c(-0.15, 0.15)))
abline(v = 40, col = 'red')
lines(sum_sliceEMO[sum_sliceEMO$label_string == 'sad', 'Mean_SKT'][[1]], col = 'blue')
lines(sum_sliceEMO[sum_sliceEMO$label_string == 'happy', 'Mean_SKT'][[1]], col = 'green')
lines(sum_sliceEMO[sum_sliceEMO$label_string == 'neutral', 'Mean_SKT'][[1]], col = 'orange')
lines(sum_sliceEMO[sum_sliceEMO$label_string == 'scared', 'Mean_SKT'][[1]], col = 'purple')
legend('topleft',inset = 0.02,legend = c('angry', 'sad', 'happy', 'neutral', 'scared'),col = c('black', 'blue', 'green', 'orange', 'purple'), cex = 0.60, lty = 1)

# DIA
plot(sum_sliceEMO[sum_sliceEMO$label_string == 'angry', 'Mean_DIA'][[1]], type = 'l', xlab = 'Slices', ylab = 'Mean DIA', ylim = range(c(-0.3, 0.3)))
abline(v = 40, col = 'red')
lines(sum_sliceEMO[sum_sliceEMO$label_string == 'sad', 'Mean_DIA'][[1]], col = 'blue')
lines(sum_sliceEMO[sum_sliceEMO$label_string == 'happy', 'Mean_DIA'][[1]], col = 'green')
lines(sum_sliceEMO[sum_sliceEMO$label_string == 'neutral', 'Mean_DIA'][[1]], col = 'orange')
lines(sum_sliceEMO[sum_sliceEMO$label_string == 'scared', 'Mean_DIA'][[1]], col = 'purple')
legend('topright',inset = 0.02,legend = c('angry', 'sad', 'happy', 'neutral', 'scared'),col = c('black', 'blue', 'green', 'orange', 'purple'), cex = 0.60, lty = 1)

```


# NA and NaN

If a variable is not present in this list, then it has zero NA or NaN values. 
```{r, include=FALSE}

sum(is.na(data$baselineCorrected_EMG_Cor_zScore))
sum(is.na(data$baselineCorrected_EMG_Zyg_zScore))
sum(is.na(data$baselineCorrected_SC_zScore))
sum(is.na(data$baselineCorrected_SKT_zScore))
sum(is.na(data$baselineCorrected_DIA_zScore))
# ID's of participants where handedness is not known
unique(data[data$Handedness == 'NaN', 1])
```



```{r}
total_data <- 5 * nrow(data)
total_missing <- sum(is.na(data$baselineCorrected_EMG_Cor_zScore)) +
  sum(is.na(data$baselineCorrected_EMG_Zyg_zScore)) + 
  sum(is.na(data$baselineCorrected_SC_zScore)) + 
  sum(is.na(data$baselineCorrected_SKT_zScore)) + 
  sum(is.na(data$baselineCorrected_DIA_zScore))

perc_EMG_Cor <- round((sum(is.na(data$baselineCorrected_EMG_Cor_zScore))/total_missing) * 100, 3)
perc_EMG_Zyg <- round((sum(is.na(data$baselineCorrected_EMG_Zyg_zScore))/total_missing) * 100, 3)
perc_SC <- round((sum(is.na(data$baselineCorrected_SC_zScore))/total_missing) * 100, 3)
perc_SKT <- round((sum(is.na(data$baselineCorrected_SKT_zScore))/total_missing) * 100, 3)
perc_DIA <- round((sum(is.na(data$baselineCorrected_DIA_zScore))/total_missing) * 100, 3)


# Of all data points of the 5 physio measures (5*525300), this percentage is missing
perc_missing_total <- round((total_missing/total_data) * 100, 3)

percentage_missing <- matrix(c(perc_EMG_Cor, perc_EMG_Zyg, perc_SC, perc_SKT, perc_DIA, perc_missing_total, sum(is.na(data$baselineCorrected_EMG_Cor_zScore)), sum(is.na(data$baselineCorrected_EMG_Zyg_zScore)), sum(is.na(data$baselineCorrected_SC_zScore)), sum(is.na(data$baselineCorrected_SKT_zScore)), sum(is.na(data$baselineCorrected_DIA_zScore)), total_missing), ncol = 6, byrow = TRUE)

colnames(percentage_missing) <- c('EMG_Cor', 'EMG_Zyg', 'SC', 'SKT', 'DIA', 'Total')
rownames(percentage_missing) <- c('Percentage:', 'Frequency:')
percentage_missing <- as.table(percentage_missing)

percentage_missing
```


```{r}
# Group by Trial and ID
data_tib <- as_tibble(data)

by_TrialID_EMG_cor <- data_tib %>% group_by(Trial, ID)
sum_cor <- by_TrialID_EMG_cor %>% summarise(Na=sum(is.na(baselineCorrected_EMG_Cor_zScore)))

by_TrialID_EMG_zyg <- data_tib %>% group_by(Trial, ID)
sum_zyg <- by_TrialID_EMG_zyg %>% summarise(Na=sum(is.na(baselineCorrected_EMG_Zyg_zScore)))

by_TrialID_SC <- data_tib %>% group_by(Trial, ID)
sum_SC <- by_TrialID_SC %>% summarise(Na = sum(is.na(baselineCorrected_SC_zScore)))

by_TrialID_SKT <- data_tib %>% group_by(Trial, ID)
sum_SKT <- by_TrialID_SKT %>% summarise(Na = sum(is.na(baselineCorrected_SKT_zScore)))

by_TrialID_DIA <- data_tib %>% group_by(Trial, ID)
sum_DIA <- by_TrialID_DIA %>% summarise(Na = sum(is.na(baselineCorrected_DIA_zScore)))

sum_DIA[sum_DIA$ID==4 & sum_DIA$Na == 0,] # only 9 rows with 0 missing for subject 4
sum_cor[sum_cor$ID==56 & sum_cor$Na == 0,] # all missings for subject 56
```

# Conditional Mean Imputation

```{r}
# Copy the dataframe
dat <- data

for(i in 1:525300){
  if(is.na(dat[i, 'baselineCorrected_EMG_Cor_zScore'])){
    dat[i, 'baselineCorrected_EMG_Cor_zScore'] = as.numeric(sum_sliceID[sum_sliceID$ID == dat[i, 'ID'] & sum_sliceID$Slice == dat[i, 'Slice'],'Mean_Cor'])
  }
}

for(i in 1:525300){
  if(is.na(dat[i, 'baselineCorrected_EMG_Zyg_zScore'])){
    dat[i, 'baselineCorrected_EMG_Zyg_zScore'] = as.numeric(sum_sliceID[sum_sliceID$ID == dat[i, 'ID'] & sum_sliceID$Slice == dat[i, 'Slice'],'Mean_Zyg'])
  }
}

for(i in 1:525300){
  if(is.na(dat[i, 'baselineCorrected_SC_zScore'])){
    dat[i, 'baselineCorrected_SC_zScore'] = as.numeric(sum_sliceID[sum_sliceID$ID == dat[i, 'ID'] & sum_sliceID$Slice == dat[i, 'Slice'],'Mean_SC'])
  }
}

for(i in 1:525300){
  if(is.na(dat[i, 'baselineCorrected_SKT_zScore'])){
    dat[i, 'baselineCorrected_SKT_zScore'] = as.numeric(sum_sliceID[sum_sliceID$ID == dat[i, 'ID'] & sum_sliceID$Slice == dat[i, 'Slice'],'Mean_SKT'])
  }
}

for(i in 1:525300){
  if(is.na(dat[i, 'baselineCorrected_DIA_zScore'])){
    dat[i, 'baselineCorrected_DIA_zScore'] = as.numeric(sum_sliceID[sum_sliceID$ID == dat[i, 'ID'] & sum_sliceID$Slice == dat[i, 'Slice'],'Mean_DIA'])
  }
}


#save(dat,file="dat.Rda")
#load("dat.Rda")

```

Some participants don't have any values for a specific trial. For example, participant 56 doesn't have any EMG cor values. 


# Making a dataframe with summarized measures

```{r}

mat <- matrix(data = NA, nrow = 68*103, ncol = 22)
colnames(mat) <- c('ID', 'Trial', 
                   'Int_stim_Cor', 'Sl_stim_Cor', 'Int_bl_Cor', 'Sl_bl_Cor',
                   'Int_stim_Zyg', 'Sl_stim_Zyg', 'Int_bl_Zyg', 'Sl_bl_Zyg',
                   'Int_stim_SC', 'Sl_stim_SC', 'Int_bl_SC','Sl_bl_SC',
                   'Int_stim_SKT', 'Sl_stim_SKT', 'Int_bl_SKT', 'Sl_bl_SKT', 
                   'Int_stim_DIA', 'Sl_stim_DIA', 'Int_bl_DIA', 'Sl_bl_DIA')

participants <- unique_subj

mat[, 'ID'] = rep(participants, each = 103)

for(i in participants){
  trials <- unique(dat[dat$ID == i, 'Trial'])
  mat[mat[, 'ID'] == i, 'Trial'] = trials
}

signal <- c('baselineCorrected_EMG_Cor_zScore',
            'baselineCorrected_EMG_Zyg_zScore',
            'baselineCorrected_SC_zScore',
            'baselineCorrected_SKT_zScore',
            'baselineCorrected_DIA_zScore')

xstim <- c(1:40)
xblank <- c(41:75)
for(r in 1:7004){
 mat[r, 'Int_stim_Cor'] = tryCatch(lm(dat[dat$ID == mat[r, 'ID'] & dat$Trial == mat[r,'Trial'],signal[1]][xstim] ~ xstim, na.action = na.fail), error=function(err){list(list(NA, NA))})[[1]][[1]]
  
  mat[r, 'Sl_stim_Cor'] = tryCatch(lm(dat[dat$ID == mat[r, 'ID'] & dat$Trial == 
mat[r, 'Trial'],signal[1]][xstim] ~ xstim, na.action = na.fail), error=function(err){list(list(NA, NA))})[[1]][[2]]
  
  mat[r, 'Int_bl_Cor'] = tryCatch(lm(dat[dat$ID == mat[r, 'ID'] & dat$Trial == 
mat[r, 'Trial'],signal[1]][xblank] ~ xblank, na.action = na.fail), error=function(err){list(list(NA, NA))})[[1]][[1]]
  
  mat[r, 'Sl_bl_Cor'] = tryCatch(lm(dat[dat$ID == mat[r, 'ID'] & dat$Trial == 
mat[r, 'Trial'],signal[1]][xblank] ~ xblank, na.action = na.fail), error=function(err){list(list(NA, NA))})[[1]][[2]]
  
  mat[r, 'Int_stim_Zyg'] = tryCatch(lm(dat[dat$ID == mat[r, 'ID'] & dat$Trial == mat[r, 'Trial'],signal[2]][xstim] ~ xstim, na.action = na.fail), error=function(err){list(list(NA, NA))})[[1]][[1]]
  
  mat[r, 'Sl_stim_Zyg'] = tryCatch(lm(dat[dat$ID == mat[r, 'ID'] & dat$Trial == 
mat[r, 'Trial'],signal[2]][xstim] ~ xstim, na.action = na.fail), error=function(err){list(list(NA, NA))})[[1]][[2]]
  
  mat[r, 'Int_bl_Zyg'] = tryCatch(lm(dat[dat$ID == mat[r, 'ID'] & dat$Trial == 
mat[r, 'Trial'],signal[2]][xblank] ~ xblank, na.action = na.fail), error=function(err){list(list(NA, NA))})[[1]][[1]]
  
  mat[r, 'Sl_bl_Zyg'] = tryCatch(lm(dat[dat$ID == mat[r, 'ID'] & dat$Trial == 
mat[r, 'Trial'],signal[2]][xblank] ~ xblank, na.action = na.fail), error=function(err){list(list(NA, NA))})[[1]][[2]]
  
  mat[r, 'Int_stim_SC'] = tryCatch(lm(dat[dat$ID == mat[r, 'ID'] & dat$Trial == 
mat[r, 'Trial'],signal[3]][xstim] ~ xstim, na.action = na.fail), error=function(err){list(list(NA, NA))})[[1]][[1]]
  
  mat[r, 'Sl_stim_SC'] = tryCatch(lm(dat[dat$ID == mat[r, 'ID'] & dat$Trial == 
mat[r, 'Trial'],signal[3]][xstim] ~ xstim, na.action = na.fail), error=function(err){list(list(NA, NA))})[[1]][[2]]
  
  mat[r, 'Int_bl_SC'] = tryCatch(lm(dat[dat$ID == mat[r, 'ID'] & dat$Trial == 
mat[r, 'Trial'],signal[3]][xblank] ~ xblank, na.action = na.fail), error=function(err){list(list(NA, NA))})[[1]][[1]]
  
  mat[r, 'Sl_bl_SC'] = tryCatch(lm(dat[dat$ID == mat[r, 'ID'] & dat$Trial == 
mat[r, 'Trial'],signal[3]][xblank] ~ xblank, na.action = na.fail), error=function(err){list(list(NA, NA))})[[1]][[2]]
  
  mat[r, 'Int_stim_SKT'] = tryCatch(lm(dat[dat$ID == mat[r, 'ID'] & dat$Trial == mat[r, 'Trial'],signal[4]][xstim] ~ xstim, na.action = na.fail), error=function(err){NA})[[1]][[1]]
  
  mat[r, 'Sl_stim_SKT'] = tryCatch(lm(dat[dat$ID == mat[r, 'ID'] & dat$Trial == 
mat[r, 'Trial'],signal[4]][xstim] ~ xstim, na.action = na.fail), error=function(err){list(list(NA, NA))})[[1]][[2]]
  
  mat[r, 'Int_bl_SKT'] = tryCatch(lm(dat[dat$ID == mat[r, 'ID'] & dat$Trial == 
mat[r, 'Trial'],signal[4]][xblank] ~ xblank, na.action = na.fail), error=function(err){list(list(NA, NA))})[[1]][[1]]
  
  mat[r, 'Sl_bl_SKT'] = tryCatch(lm(dat[dat$ID == mat[r, 'ID'] & dat$Trial == 
mat[r, 'Trial'],signal[4]][xblank] ~ xblank, na.action = na.fail), error=function(err){list(list(NA, NA))})[[1]][[2]]
  
  mat[r, 'Int_stim_DIA'] = tryCatch(lm(dat[dat$ID == mat[r, 'ID'] & dat$Trial == mat[r, 'Trial'],signal[5]][xstim] ~ xstim, na.action = na.fail), error=function(err){list(list(NA, NA))})[[1]][[1]]
  
  mat[r, 'Sl_stim_DIA'] = tryCatch(lm(dat[dat$ID == mat[r, 'ID'] & dat$Trial == 
mat[r, 'Trial'],signal[5]][xstim] ~ xstim, na.action = na.fail), error=function(err){list(list(NA, NA))})[[1]][[2]]
  
  mat[r, 'Int_bl_DIA'] = tryCatch(lm(dat[dat$ID == mat[r, 'ID'] & dat$Trial == 
mat[r, 'Trial'],signal[5]][xblank] ~ xblank, na.action = na.fail), error=function(err){list(list(NA, NA))})[[1]][[1]]
  
  mat[r, 'Sl_bl_DIA'] = tryCatch(lm(dat[dat$ID == mat[r, 'ID'] & dat$Trial == 
mat[r, 'Trial'],signal[5]][xblank] ~ xblank, na.action = na.fail), error=function(err){list(list(NA, NA))})[[1]][[2]]
}

# To save the matrix
library(MASS)
write.matrix(mat, file = "mat_imputed", sep = " ")
mat_read <- read.table("mat_imputed", header = TRUE)


```

For every participant, we calculated the slope and intercept for that person per trial per physiological signal. This way, the multilevel model no longer has slices as a level but only participants and trials. This is necessary because the outcome variable (emotion) needs to be on the same level in a multilevel multinomial model. However, in the initial set up, slices were the lowest level but the outcome variable emotion label was on the level of trials. So the data is sort of downsized and now every trial has 20 values (every signal has a slope and intercept for the stimulus window and a slope and intercept for the blank window) capturing the data in the slices. 

