---
title: "Initial_DataAnalysis"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, error = TRUE, cache = TRUE)
library(knitr)
library(readxl)
library(tidyverse)

# Loading the data
data <- read.csv('analysisTable_zScore_EQ.txt')
```

# Inspecting the data

```{r}
head(data)
summary(data)

# Colnames
names(data)
```

No cases of Autism Specturm Disorder. However, max score of LSAS\_overall is 83 which indicates Social Anxiety. 

```{r}
unique(data[data$LSAS_overall > 60, 'ID']) # Persons with Social Anxiety 

#unique(data[data$ID==7, 'LSAS_overall']) #79
#unique(data[data$ID==8, 'LSAS_overall']) #66
#unique(data[data$ID==15, 'LSAS_overall']) #76
#unique(data[data$ID==16, 'LSAS_overall']) #77
#unique(data[data$ID==19, 'LSAS_overall']) #76
#unique(data[data$ID==21, 'LSAS_overall']) #77
#unique(data[data$ID==26, 'LSAS_overall']) #83
#unique(data[data$ID==59, 'LSAS_overall']) #62
#unique(data[data$ID==60, 'LSAS_overall']) #65

```


```{r}
#unique(data$EmoCat_string)
#unique(data$label_string)

#sum(data$EmoCat_string == 'scared') #81600
#sum(data$EmoCat_string == 'scared' & data$label_string == 'scared') #71550

#sum(data$EmoCat_string == 'sad') #81600
#sum(data$EmoCat_string == 'sad' & data$label_string == 'sad') #65925

#sum(data$EmoCat_string == 'angry') #81600
#sum(data$EmoCat_string == 'angry' & data$label_string == 'angry') #69225

#sum(data$EmoCat_string == 'happy') #81600
#sum(data$EmoCat_string == 'happy' & data$label_string == 'happy') #63750

#sum(data$EmoCat_string == 'neutral') #81600
#sum(data$EmoCat_string == 'neutral' & data$label_string == 'neutral') #68100

```


# Participants

```{r}
unique_subj <- unlist(unique(data[1]), use.names = FALSE)
paste0('There are ', length(unique_subj), ' subjects.')

cnt_obs_subj <- numeric()
for (i in 1:length(unique_subj)) {
  cnt_obs_subj[i] <- sum(data[1] == unique_subj[i])
}
unique(cnt_obs_subj) # Every subject has 7725 measures
```

# Trials

```{r}
unique_trial <- sort(unlist(unique(data[2]), use.names = FALSE))
paste0('There are ', length(unique_trial), ' trials.') 

cnt_trials <- numeric()
for (i in 1:length(unique_trial)) {
  cnt_trials[i] <- sum(data[2] == unique_trial[i])
}
unique(cnt_trials) # There are 5025, 5100, 4950, 4875 meaures for trials
hist(cnt_trials)
#unique(data[data$Trial == 1,'ID']) # participant 7 has no trial 1
#unique(data[data$Trial == 2,'ID']) # participant 61 has no trial 2
#unique(data[data$Trial == 4,'ID']) # participants 15 and 33 have no trial 4
#unique(data[data$Trial == 5,'ID']) # participants 11, 20 and 66 have no trial 5
#unique(data[data$Trial == 7,'ID']) # participant 17 has no trial 7
#unique(data[data$Trial == 16,'ID']) # participant 37 has no trial 16
#unique(data[data$Trial == 18,'ID']) # participants 29, 38 and 40 have no trial 18
#unique(data[data$Trial == 21,'ID']) # participant 10 has no trial 21
#unique(data[data$Trial == 22,'ID']) # participant 19 has no trial 22
#unique(data[data$Trial == 24,'ID']) # participant 45 has no trial 24
#unique(data[data$Trial == 25,'ID']) # participants 18 and 25 have no trial 25
#unique(data[data$Trial == 26,'ID']) # participant 12 has no trial 26
#unique(data[data$Trial == 27,'ID']) # participant 57 has no trial 27
#unique(data[data$Trial == 28,'ID']) # participant 71 has no trial 28
#unique(data[data$Trial == 31,'ID']) # participant 36 has no trial 31
#unique(data[data$Trial == 36,'ID']) # participant 26 has no trial 36
#unique(data[data$Trial == 38,'ID']) # participant 68 has no trial 38
#unique(data[data$Trial == 43,'ID']) # participant 43 has no trial 43
#unique(data[data$Trial == 47,'ID']) # participant 69 has no trial 47
#unique(data[data$Trial == 50,'ID']) # participant 4 has no trial 50
#unique(data[data$Trial == 52,'ID']) # participant 58 has no trial 52
#unique(data[data$Trial == 54,'ID']) # participant 41 has no trial 54
#unique(data[data$Trial == 55,'ID']) # participants 8 and 54 have no trial 55
#unique(data[data$Trial == 56,'ID']) # participant 59 has no trial 56
#unique(data[data$Trial == 58,'ID']) # participant 28 has no trial 58
#unique(data[data$Trial == 60,'ID']) # participant 22 has no trial 60
#unique(data[data$Trial == 61,'ID']) # participants 6, 30 and 32 have no trial 61
#unique(data[data$Trial == 65,'ID']) # participant 39 has no trial 65
#unique(data[data$Trial == 66,'ID']) # participants 49 and 64 have no trial 66
#unique(data[data$Trial == 67,'ID']) # participant 46 has no trial 67
#unique(data[data$Trial == 68,'ID']) # participant 48 has no trial 68
#unique(data[data$Trial == 70,'ID']) # participants 44 and 62 have no trial 70
#unique(data[data$Trial == 72,'ID']) # participants 23 and 63 have no trial 72
#unique(data[data$Trial == 76,'ID']) # participants 24 and 65 have no trial 76
#unique(data[data$Trial == 77,'ID']) # participant 34 has no trial 77
#unique(data[data$Trial == 78,'ID']) # participant 60 has no trial 78
#unique(data[data$Trial == 79,'ID']) # participant 55 has no trial 79
#unique(data[data$Trial == 80,'ID']) # participant 51 has no trial 80
#unique(data[data$Trial == 81,'ID']) # participant 42 has no trial 81
#unique(data[data$Trial == 83,'ID']) # participant 9 has no trial 83
#unique(data[data$Trial == 86,'ID']) # participants 13 and 16 have no trial 86
#unique(data[data$Trial == 87,'ID']) # participant 21 has no trial 87
#unique(data[data$Trial == 89,'ID']) # participant 56 has no trial 89
#unique(data[data$Trial == 92,'ID']) # participants 52, 53 and 67 have no trial 92
#unique(data[data$Trial == 94,'ID']) # participant 47 has no trial 94
#unique(data[data$Trial == 95,'ID']) # participant 14 has no trial 95
#unique(data[data$Trial == 97,'ID']) # participant 70 has no trial 97
#unique(data[data$Trial == 98,'ID']) # participant 27 has no trial 98
#unique(data[data$Trial == 99,'ID']) # participant 31 has no trial 99
#unique(data[data$Trial == 100,'ID']) # participant 5 has no trial 100
#unique(data[data$Trial == 101,'ID']) # participant 35 has no trial 101
#unique(data[data$Trial == 102,'ID']) # participant 50 has no trial 102

```

Every participant misses one trial.


# Means

```{r, include= FALSE}
mean(data$Age)
mean(data$AQ_overall)
mean(data$LSAS_overall)
mean(data$EQ_overall)
mean(data$baselineCorrected_EMG_Cor_zScore, na.rm = TRUE) # With NA's removed
mean(data$baselineCorrected_EMG_Zyg_zScore, na.rm = TRUE) # With NA's removed
mean(data$baselineCorrected_SC_zScore, na.rm = TRUE) # With NA's removed
mean(data$baselineCorrected_SKT_zScore, na.rm = TRUE) # With NA's removed
mean(data$baselineCorrected_DIA_zScore, na.rm = TRUE) # With NA's removed

```


```{r}
# Group by Slice
data_tib <- as_tibble(data)

by_Slice <- data_tib %>% group_by(Slice)

# Means of signals per slice
sum_slice <- by_Slice %>% summarise(Mean_Cor = mean(baselineCorrected_EMG_Cor_zScore, na.rm = TRUE), Mean_Zyg = mean(baselineCorrected_EMG_Zyg_zScore, na.rm = TRUE), Mean_SC = mean(baselineCorrected_SC_zScore, na.rm = TRUE), Mean_SKT = mean(baselineCorrected_SKT_zScore, na.rm = TRUE), Mean_DIA = mean(baselineCorrected_DIA_zScore, na.rm = TRUE))

sum_slice

```


```{r}
# Group by Slice, Emo
data_tib <- as_tibble(data)

by_SliceEMO <- data_tib %>% group_by(Slice, label_string)

# Means of signals per slice per labelled emotion
sum_sliceEMO <- by_SliceEMO %>% summarise(Mean_Cor = mean(baselineCorrected_EMG_Cor_zScore, na.rm = TRUE), Mean_Zyg = mean(baselineCorrected_EMG_Zyg_zScore, na.rm = TRUE), Mean_SC = mean(baselineCorrected_SC_zScore, na.rm = TRUE), Mean_SKT = mean(baselineCorrected_SKT_zScore, na.rm = TRUE), Mean_DIA = mean(baselineCorrected_DIA_zScore, na.rm = TRUE))

sum_sliceEMO


```



```{r}
# Group by Slice and ID
by_SliceID <- data_tib %>% group_by(Slice, ID)

# Means of signal per ID per slice
sum_sliceID <- by_SliceID %>% summarise(Mean_Cor = mean(baselineCorrected_EMG_Cor_zScore, na.rm = TRUE), Mean_Zyg = mean(baselineCorrected_EMG_Zyg_zScore, na.rm = TRUE), Mean_SC = mean(baselineCorrected_SC_zScore, na.rm = TRUE), Mean_SKT = mean(baselineCorrected_SKT_zScore, na.rm = TRUE), Mean_DIA = mean(baselineCorrected_DIA_zScore, na.rm = TRUE))

sum_sliceID


```


# Descriptives and plots

```{r, include=FALSE}
# Age
boxplot(data$Age)

# Gender
plot(data$Gender)

# Handedness
plot(data$Handedness)
unique(data[c(data$Handedness == 'NaN'), 'ID']) # ID with missing Handedness

# EMG Corrugator
xstim <- c(1:40)
xblank <- c(41:75)
mean_cor_stim <- sum_slice$Mean_Cor[1:40]
mean_cor_blank <- sum_slice$Mean_Cor[41:75]
reg_stim <- lm(mean_cor_stim ~ xstim)
reg_blank <- lm(mean_cor_blank ~ xblank)

plot(sum_slice$Mean_Cor, type = 'l', xlab = 'Slices', ylab = 'Mean EMG_Cor')
abline(v = 40, col = 'red')
lines(reg_stim$fitted.values, col = 'blue')
lines(x = c(40:74), reg_blank$fitted.values, col = 'green')

# EMG Zygomaticus
xstim <- c(1:40)
xblank <- c(41:75)
mean_zyg_stim <- sum_slice$Mean_Zyg[1:40]
mean_zyg_blank <- sum_slice$Mean_Zyg[41:75]
reg_stim <- lm(mean_zyg_stim ~ xstim)
reg_blank <- lm(mean_zyg_blank ~ xblank)

plot(sum_slice$Mean_Zyg, type = 'l', xlab = 'Slices', ylab = 'Mean EMG_Zyg')
abline(v = 40, col = 'red')
lines(reg_stim$fitted.values, col = 'blue')
lines(x = c(40:74), reg_blank$fitted.values, col = 'green')

# Skin Conductance
xstim <- c(1:40)
xblank <- c(41:75)
mean_sc_stim <- sum_slice$Mean_SC[1:40]
mean_sc_blank <- sum_slice$Mean_SC[41:75]
reg_stim <- lm(mean_sc_stim ~ xstim)
reg_blank <- lm(mean_sc_blank ~ xblank)

plot(sum_slice$Mean_SC, type = 'l', xlab = 'Slices', ylab = 'Mean SC')
abline(v = 40, col = 'red')
lines(reg_stim$fitted.values, col = 'blue')
lines(x = c(40:74), reg_blank$fitted.values, col = 'green')

# Skin Temperature
xstim <- c(1:40)
xblank <- c(41:75)
mean_skt_stim <- sum_slice$Mean_SKT[1:40]
mean_skt_blank <- sum_slice$Mean_SKT[41:75]
reg_stim <- lm(mean_skt_stim ~ xstim)
reg_blank <- lm(mean_skt_blank ~ xblank)

plot(sum_slice$Mean_SKT, type = 'l', xlab = 'Slices', ylab = 'Mean SKT')
abline(v = 40, col = 'red')
lines(reg_stim$fitted.values, col = 'blue')
lines(x = c(40:74), reg_blank$fitted.values, col = 'green')

# Pupil Diameter
xstim <- c(1:40)
xblank <- c(41:75)
mean_dia_stim <- sum_slice$Mean_DIA[1:40]
mean_dia_blank <- sum_slice$Mean_DIA[41:75]
reg_stim <- lm(mean_dia_stim ~ xstim)
reg_blank <- lm(mean_dia_blank ~ xblank)

plot(sum_slice$Mean_DIA, type = 'l', xlab = 'Slices', ylab = 'Mean DIA')
abline(v = 40, col = 'red')
lines(reg_stim$fitted.values, col = 'blue')
lines(x = c(40:74), reg_blank$fitted.values, col = 'green')
```




```{r}
# Plot mean signal score per emotion

# EMG Cor
plot(sum_sliceEMO[sum_sliceEMO$label_string == 'angry', 'Mean_Cor'][[1]], type = 'l', xlab = 'Slices', ylab = 'Mean EMG_Cor', ylim = range(c(-0.12, 0.12)))
abline(v = 40, col = 'red')
lines(sum_sliceEMO[sum_sliceEMO$label_string == 'sad', 'Mean_Cor'][[1]], col = 'blue')
lines(sum_sliceEMO[sum_sliceEMO$label_string == 'happy', 'Mean_Cor'][[1]], col = 'green')
lines(sum_sliceEMO[sum_sliceEMO$label_string == 'neutral', 'Mean_Cor'][[1]], col = 'orange')
lines(sum_sliceEMO[sum_sliceEMO$label_string == 'scared', 'Mean_Cor'][[1]], col = 'purple')
legend('topright',inset = 0.02,legend = c('angry', 'sad', 'happy', 'neutral', 'scared'),col = c('black', 'blue', 'green', 'orange', 'purple'), cex = 0.60, lty = 1)

# EMG Zyg
plot(sum_sliceEMO[sum_sliceEMO$label_string == 'angry', 'Mean_Zyg'][[1]], type = 'l', xlab = 'Slices', ylab = 'Mean EMG_Zyg', ylim = range(c(-0.1, 0.15)))
abline(v = 40, col = 'red')
lines(sum_sliceEMO[sum_sliceEMO$label_string == 'sad', 'Mean_Zyg'][[1]], col = 'blue')
lines(sum_sliceEMO[sum_sliceEMO$label_string == 'happy', 'Mean_Zyg'][[1]], col = 'green')
lines(sum_sliceEMO[sum_sliceEMO$label_string == 'neutral', 'Mean_Zyg'][[1]], col = 'orange')
lines(sum_sliceEMO[sum_sliceEMO$label_string == 'scared', 'Mean_Zyg'][[1]], col = 'purple')
legend('topleft',inset = 0.02,legend = c('angry', 'sad', 'happy', 'neutral', 'scared'),col = c('black', 'blue', 'green', 'orange', 'purple'), cex = 0.50, lty = 1)

# SC
plot(sum_sliceEMO[sum_sliceEMO$label_string == 'angry', 'Mean_SC'][[1]], type = 'l', xlab = 'Slices', ylab = 'Mean SC', ylim = range(c(-0.15, 0.15)))
abline(v = 40, col = 'red')
lines(sum_sliceEMO[sum_sliceEMO$label_string == 'sad', 'Mean_SC'][[1]], col = 'blue')
lines(sum_sliceEMO[sum_sliceEMO$label_string == 'happy', 'Mean_SC'][[1]], col = 'green')
lines(sum_sliceEMO[sum_sliceEMO$label_string == 'neutral', 'Mean_SC'][[1]], col = 'orange')
lines(sum_sliceEMO[sum_sliceEMO$label_string == 'scared', 'Mean_SC'][[1]], col = 'purple')
legend('topright',inset = 0.02,legend = c('angry', 'sad', 'happy', 'neutral', 'scared'),col = c('black', 'blue', 'green', 'orange', 'purple'), cex = 0.60, lty = 1)

# SKT
plot(sum_sliceEMO[sum_sliceEMO$label_string == 'angry', 'Mean_SKT'][[1]], type = 'l', xlab = 'Slices', ylab = 'Mean SKT', ylim = range(c(-0.15, 0.15)))
abline(v = 40, col = 'red')
lines(sum_sliceEMO[sum_sliceEMO$label_string == 'sad', 'Mean_SKT'][[1]], col = 'blue')
lines(sum_sliceEMO[sum_sliceEMO$label_string == 'happy', 'Mean_SKT'][[1]], col = 'green')
lines(sum_sliceEMO[sum_sliceEMO$label_string == 'neutral', 'Mean_SKT'][[1]], col = 'orange')
lines(sum_sliceEMO[sum_sliceEMO$label_string == 'scared', 'Mean_SKT'][[1]], col = 'purple')
legend('topleft',inset = 0.02,legend = c('angry', 'sad', 'happy', 'neutral', 'scared'),col = c('black', 'blue', 'green', 'orange', 'purple'), cex = 0.60, lty = 1)

# DIA
plot(sum_sliceEMO[sum_sliceEMO$label_string == 'angry', 'Mean_DIA'][[1]], type = 'l', xlab = 'Slices', ylab = 'Mean DIA', ylim = range(c(-0.3, 0.3)))
abline(v = 40, col = 'red')
lines(sum_sliceEMO[sum_sliceEMO$label_string == 'sad', 'Mean_DIA'][[1]], col = 'blue')
lines(sum_sliceEMO[sum_sliceEMO$label_string == 'happy', 'Mean_DIA'][[1]], col = 'green')
lines(sum_sliceEMO[sum_sliceEMO$label_string == 'neutral', 'Mean_DIA'][[1]], col = 'orange')
lines(sum_sliceEMO[sum_sliceEMO$label_string == 'scared', 'Mean_DIA'][[1]], col = 'purple')
legend('topright',inset = 0.02,legend = c('angry', 'sad', 'happy', 'neutral', 'scared'),col = c('black', 'blue', 'green', 'orange', 'purple'), cex = 0.60, lty = 1)

```



```{r, include=FALSE}
# Plot subject 4 trial 1, EMG_Cor

id4trial1_stim <- data[data$ID ==4 & data$Trial ==1,'baselineCorrected_EMG_Cor'][1:40]
xstim <- c(1:40)
reg_stim <- lm(id4trial1_stim ~ xstim)

id4trial1_bl <- data[data$ID ==4 & data$Trial==1,'baselineCorrected_EMG_Cor'][41:75]
xbl <- c(41:75)
reg_bl <- lm(id4trial1_bl ~ xbl)

plot(data[data$ID == 4 & data$Trial==1, 'baselineCorrected_EMG_Cor'], type = 'l')
abline(v = 40, col = 'red')
lines(reg_stim$fitted.values, col = 'blue')
lines(x = c(40:74), reg_bl$fitted.values, col = 'green')

```


# NA and NaN

If a variable is not present in this list, then it has zero NA or NaN values. 
```{r, include=FALSE}

sum(is.na(data$baselineCorrected_EMG_Cor_zScore))
sum(is.na(data$baselineCorrected_EMG_Zyg_zScore))
sum(is.na(data$baselineCorrected_SC_zScore))
sum(is.na(data$baselineCorrected_SKT_zScore))
sum(is.na(data$baselineCorrected_DIA_zScore))
# ID's of participants where handedness is not known
unique(data[data$Handedness == 'NaN', 1])
```



```{r}
total_data <- 5 * nrow(data)
total_missing <- sum(is.na(data$baselineCorrected_EMG_Cor_zScore)) +
  sum(is.na(data$baselineCorrected_EMG_Zyg_zScore)) + 
  sum(is.na(data$baselineCorrected_SC_zScore)) + 
  sum(is.na(data$baselineCorrected_SKT_zScore)) + 
  sum(is.na(data$baselineCorrected_DIA_zScore))

perc_EMG_Cor <- round((sum(is.na(data$baselineCorrected_EMG_Cor_zScore))/total_missing) * 100, 3)
perc_EMG_Zyg <- round((sum(is.na(data$baselineCorrected_EMG_Zyg_zScore))/total_missing) * 100, 3)
perc_SC <- round((sum(is.na(data$baselineCorrected_SC_zScore))/total_missing) * 100, 3)
perc_SKT <- round((sum(is.na(data$baselineCorrected_SKT_zScore))/total_missing) * 100, 3)
perc_DIA <- round((sum(is.na(data$baselineCorrected_DIA_zScore))/total_missing) * 100, 3)


# Of all data points of the 5 physio measures (5*525300), this percentage is missing
perc_missing_total <- round((total_missing/total_data) * 100, 3)

percentage_missing <- matrix(c(perc_EMG_Cor, perc_EMG_Zyg, perc_SC, perc_SKT, perc_DIA, perc_missing_total, sum(is.na(data$baselineCorrected_EMG_Cor_zScore)), sum(is.na(data$baselineCorrected_EMG_Zyg_zScore)), sum(is.na(data$baselineCorrected_SC_zScore)), sum(is.na(data$baselineCorrected_SKT_zScore)), sum(is.na(data$baselineCorrected_DIA_zScore)), total_missing), ncol = 6, byrow = TRUE)

colnames(percentage_missing) <- c('EMG_Cor', 'EMG_Zyg', 'SC', 'SKT', 'DIA', 'Total')
rownames(percentage_missing) <- c('Percentage:', 'Frequency:')
percentage_missing <- as.table(percentage_missing)

percentage_missing
```


```{r}
# Group by Trial and ID
data_tib <- as_tibble(data)

by_TrialID_EMG_cor <- data_tib %>% group_by(Trial, ID)
sum_cor <- by_TrialID_EMG_cor %>% summarise(Na=sum(is.na(baselineCorrected_EMG_Cor_zScore)))

by_TrialID_EMG_zyg <- data_tib %>% group_by(Trial, ID)
sum_zyg <- by_TrialID_EMG_zyg %>% summarise(Na=sum(is.na(baselineCorrected_EMG_Zyg_zScore)))

by_TrialID_SC <- data_tib %>% group_by(Trial, ID)
sum_SC <- by_TrialID_SC %>% summarise(Na = sum(is.na(baselineCorrected_SC_zScore)))

by_TrialID_SKT <- data_tib %>% group_by(Trial, ID)
sum_SKT <- by_TrialID_SKT %>% summarise(Na = sum(is.na(baselineCorrected_SKT_zScore)))

by_TrialID_DIA <- data_tib %>% group_by(Trial, ID)
sum_DIA <- by_TrialID_DIA %>% summarise(Na = sum(is.na(baselineCorrected_DIA_zScore)))

sum_DIA[sum_DIA$ID==4 & sum_DIA$Na == 0,] # only 9 rows with 0 missing
sum_cor[sum_cor$ID==56 & sum_cor$Na == 0,] # all missings
```

# Conditional Mean Imputation

```{r}
dat <- data

for(i in 1:525300){
  if(is.na(dat[i, 'baselineCorrected_EMG_Cor_zScore'])){
    dat[i, 'baselineCorrected_EMG_Cor_zScore'] = as.numeric(sum_sliceID[sum_sliceID$ID == dat[i, 'ID'] & sum_sliceID$Slice == dat[i, 'Slice'],'Mean_Cor'])
  }
}

for(i in 1:525300){
  if(is.na(dat[i, 'baselineCorrected_EMG_Zyg_zScore'])){
    dat[i, 'baselineCorrected_EMG_Zyg_zScore'] = as.numeric(sum_sliceID[sum_sliceID$ID == dat[i, 'ID'] & sum_sliceID$Slice == dat[i, 'Slice'],'Mean_Zyg'])
  }
}

for(i in 1:525300){
  if(is.na(dat[i, 'baselineCorrected_SC_zScore'])){
    dat[i, 'baselineCorrected_SC_zScore'] = as.numeric(sum_sliceID[sum_sliceID$ID == dat[i, 'ID'] & sum_sliceID$Slice == dat[i, 'Slice'],'Mean_SC'])
  }
}

for(i in 1:525300){
  if(is.na(dat[i, 'baselineCorrected_SKT_zScore'])){
    dat[i, 'baselineCorrected_SKT_zScore'] = as.numeric(sum_sliceID[sum_sliceID$ID == dat[i, 'ID'] & sum_sliceID$Slice == dat[i, 'Slice'],'Mean_SKT'])
  }
}

for(i in 1:525300){
  if(is.na(dat[i, 'baselineCorrected_DIA_zScore'])){
    dat[i, 'baselineCorrected_DIA_zScore'] = as.numeric(sum_sliceID[sum_sliceID$ID == dat[i, 'ID'] & sum_sliceID$Slice == dat[i, 'Slice'],'Mean_DIA'])
  }
}


#save(dat,file="dat.Rda")

load("dat.Rda")


```

Some participants don't have any values for a specific trial. For example, participant 56 doesn't have any EMG cor values. 

# Unconditional Mean Imputation

```{r, include= FALSE}
da <- data

for(i in 1:525300){
  if(is.na(da[i, 'baselineCorrected_EMG_Cor_zScore'])){
    da[i, 'baselineCorrected_EMG_Cor_zScore'] = as.numeric(sum_slice[sum_slice$Slice == da[i, 'Slice'],'Mean_Cor'])
  }
}

for(i in 1:525300){
  if(is.na(da[i, 'baselineCorrected_EMG_Zyg_zScore'])){
    da[i, 'baselineCorrected_EMG_Zyg_zScore'] = as.numeric(sum_slice[sum_slice$Slice == da[i, 'Slice'],'Mean_Zyg'])
  }
}

for(i in 1:525300){
  if(is.na(da[i, 'baselineCorrected_SC_zScore'])){
    da[i, 'baselineCorrected_SC_zScore'] = as.numeric(sum_slice[sum_slice$Slice == da[i, 'Slice'],'Mean_SC'])
  }
}

for(i in 1:525300){
  if(is.na(da[i, 'baselineCorrected_SKT_zScore'])){
    da[i, 'baselineCorrected_SKT_zScore'] = as.numeric(sum_slice[sum_slice$Slice == da[i, 'Slice'],'Mean_SKT'])
  }
}

for(i in 1:525300){
  if(is.na(da[i, 'baselineCorrected_DIA_zScore'])){
    da[i, 'baselineCorrected_DIA_zScore'] = as.numeric(sum_slice[sum_slice$Slice == da[i, 'Slice'],'Mean_DIA'])
  }
}

```

Not sure whether this is possible because design is maybe unbalanced (unequal trials). 
# Making a dataframe with summarized measures

```{r}

mat <- matrix(data = NA, nrow = 68*103, ncol = 22)
colnames(mat) <- c('ID', 'Trial', 
                   'Int_stim_Cor', 'Sl_stim_Cor', 'Int_bl_Cor', 'Sl_bl_Cor',
                   'Int_stim_Zyg', 'Sl_stim_Zyg', 'Int_bl_Zyg', 'Sl_bl_Zyg',
                   'Int_stim_SC', 'Sl_stim_SC', 'Int_bl_SC','Sl_bl_SC',
                   'Int_stim_SKT', 'Sl_stim_SKT', 'Int_bl_SKT', 'Sl_bl_SKT', 
                   'Int_stim_DIA', 'Sl_stim_DIA', 'Int_bl_DIA', 'Sl_bl_DIA')

participants <- unique_subj

mat[, 'ID'] = rep(participants, each = 103)

for(i in participants){
  trials <- unique(dat[dat$ID == i, 'Trial'])
  mat[mat[, 'ID'] == i, 'Trial'] = trials
}

signal <- c('baselineCorrected_EMG_Cor_zScore',
            'baselineCorrected_EMG_Zyg_zScore',
            'baselineCorrected_SC_zScore',
            'baselineCorrected_SKT_zScore',
            'baselineCorrected_DIA_zScore')

xstim <- c(1:40)
xblank <- c(41:75)
for(r in 1:7004){
 mat[r, 'Int_stim_Cor'] = tryCatch(lm(dat[dat$ID == mat[r, 'ID'] & dat$Trial == mat[r,'Trial'],signal[1]][xstim] ~ xstim, na.action = na.fail), error=function(err){list(list(NA, NA))})[[1]][[1]]
  
  mat[r, 'Sl_stim_Cor'] = tryCatch(lm(dat[dat$ID == mat[r, 'ID'] & dat$Trial == 
mat[r, 'Trial'],signal[1]][xstim] ~ xstim, na.action = na.fail), error=function(err){list(list(NA, NA))})[[1]][[2]]
  
  mat[r, 'Int_bl_Cor'] = tryCatch(lm(dat[dat$ID == mat[r, 'ID'] & dat$Trial == 
mat[r, 'Trial'],signal[1]][xblank] ~ xblank, na.action = na.fail), error=function(err){list(list(NA, NA))})[[1]][[1]]
  
  mat[r, 'Sl_bl_Cor'] = tryCatch(lm(dat[dat$ID == mat[r, 'ID'] & dat$Trial == 
mat[r, 'Trial'],signal[1]][xblank] ~ xblank, na.action = na.fail), error=function(err){list(list(NA, NA))})[[1]][[2]]
  
  mat[r, 'Int_stim_Zyg'] = tryCatch(lm(dat[dat$ID == mat[r, 'ID'] & dat$Trial == mat[r, 'Trial'],signal[2]][xstim] ~ xstim, na.action = na.fail), error=function(err){list(list(NA, NA))})[[1]][[1]]
  
  mat[r, 'Sl_stim_Zyg'] = tryCatch(lm(dat[dat$ID == mat[r, 'ID'] & dat$Trial == 
mat[r, 'Trial'],signal[2]][xstim] ~ xstim, na.action = na.fail), error=function(err){list(list(NA, NA))})[[1]][[2]]
  
  mat[r, 'Int_bl_Zyg'] = tryCatch(lm(dat[dat$ID == mat[r, 'ID'] & dat$Trial == 
mat[r, 'Trial'],signal[2]][xblank] ~ xblank, na.action = na.fail), error=function(err){list(list(NA, NA))})[[1]][[1]]
  
  mat[r, 'Sl_bl_Zyg'] = tryCatch(lm(dat[dat$ID == mat[r, 'ID'] & dat$Trial == 
mat[r, 'Trial'],signal[2]][xblank] ~ xblank, na.action = na.fail), error=function(err){list(list(NA, NA))})[[1]][[2]]
  
  mat[r, 'Int_stim_SC'] = tryCatch(lm(dat[dat$ID == mat[r, 'ID'] & dat$Trial == 
mat[r, 'Trial'],signal[3]][xstim] ~ xstim, na.action = na.fail), error=function(err){list(list(NA, NA))})[[1]][[1]]
  
  mat[r, 'Sl_stim_SC'] = tryCatch(lm(dat[dat$ID == mat[r, 'ID'] & dat$Trial == 
mat[r, 'Trial'],signal[3]][xstim] ~ xstim, na.action = na.fail), error=function(err){list(list(NA, NA))})[[1]][[2]]
  
  mat[r, 'Int_bl_SC'] = tryCatch(lm(dat[dat$ID == mat[r, 'ID'] & dat$Trial == 
mat[r, 'Trial'],signal[3]][xblank] ~ xblank, na.action = na.fail), error=function(err){list(list(NA, NA))})[[1]][[1]]
  
  mat[r, 'Sl_bl_SC'] = tryCatch(lm(dat[dat$ID == mat[r, 'ID'] & dat$Trial == 
mat[r, 'Trial'],signal[3]][xblank] ~ xblank, na.action = na.fail), error=function(err){list(list(NA, NA))})[[1]][[2]]
  
  mat[r, 'Int_stim_SKT'] = tryCatch(lm(dat[dat$ID == mat[r, 'ID'] & dat$Trial == mat[r, 'Trial'],signal[4]][xstim] ~ xstim, na.action = na.fail), error=function(err){NA})[[1]][[1]]
  
  mat[r, 'Sl_stim_SKT'] = tryCatch(lm(dat[dat$ID == mat[r, 'ID'] & dat$Trial == 
mat[r, 'Trial'],signal[4]][xstim] ~ xstim, na.action = na.fail), error=function(err){list(list(NA, NA))})[[1]][[2]]
  
  mat[r, 'Int_bl_SKT'] = tryCatch(lm(dat[dat$ID == mat[r, 'ID'] & dat$Trial == 
mat[r, 'Trial'],signal[4]][xblank] ~ xblank, na.action = na.fail), error=function(err){list(list(NA, NA))})[[1]][[1]]
  
  mat[r, 'Sl_bl_SKT'] = tryCatch(lm(dat[dat$ID == mat[r, 'ID'] & dat$Trial == 
mat[r, 'Trial'],signal[4]][xblank] ~ xblank, na.action = na.fail), error=function(err){list(list(NA, NA))})[[1]][[2]]
  
  mat[r, 'Int_stim_DIA'] = tryCatch(lm(dat[dat$ID == mat[r, 'ID'] & dat$Trial == mat[r, 'Trial'],signal[5]][xstim] ~ xstim, na.action = na.fail), error=function(err){list(list(NA, NA))})[[1]][[1]]
  
  mat[r, 'Sl_stim_DIA'] = tryCatch(lm(dat[dat$ID == mat[r, 'ID'] & dat$Trial == 
mat[r, 'Trial'],signal[5]][xstim] ~ xstim, na.action = na.fail), error=function(err){list(list(NA, NA))})[[1]][[2]]
  
  mat[r, 'Int_bl_DIA'] = tryCatch(lm(dat[dat$ID == mat[r, 'ID'] & dat$Trial == 
mat[r, 'Trial'],signal[5]][xblank] ~ xblank, na.action = na.fail), error=function(err){list(list(NA, NA))})[[1]][[1]]
  
  mat[r, 'Sl_bl_DIA'] = tryCatch(lm(dat[dat$ID == mat[r, 'ID'] & dat$Trial == 
mat[r, 'Trial'],signal[5]][xblank] ~ xblank, na.action = na.fail), error=function(err){list(list(NA, NA))})[[1]][[2]]
}

library(MASS)
write.matrix(mat, file = "mat_imputed", sep = " ")
mat_read <- read.table("mat_imputed", header = TRUE)


#sum(is.na(mat[,3])) #103 missing for Int_stim_Cor     Participant 56
#sum(is.na(mat[,4])) #103 missing for Sl_stim_Cor
#sum(is.na(mat[,5])) #103 missing for Int_bl_Cor
#sum(is.na(mat[,6])) #103 missing for Sl_bl_Cor
#sum(is.na(mat[,19])) #309 missing for Int_stim_DIA    Participants 25, 26 and 27
#sum(is.na(mat[,20])) #309 missing for Sl_stim_DIA
#sum(is.na(mat[,21])) #309 missing for Int_bl_DIA
#sum(is.na(mat[,22])) #309 missing for Sl_bl_DIA


```

For every participant, we calculated the slope and intercept for that person per trial per physiological signal. This way, the multilevel model no longer has slices as a level but only participants and trials. This is necessary because the outcome variable (emotion) needs to be on the same level in a multilevel multinomial model. However, in the initial set up, slices were the lowest level but the outcome variable emotion label was on the level of trials. So the data is sort of downsized and now every trial has 20 values (every signal has a slope and intercept for the stimulus window and a slope and intercept for the blank window) capturing the data in the slices. 

# Extending matrix

```{r}
dat_uniq_label <- unique(dat[, c('ID', 'Trial', 'label_string')])
mat_label <- merge(mat_read, dat_uniq_label, by = c('ID', 'Trial'), sort=FALSE)
dat_uniq_labl1 <- unique(dat[, c('ID', 'Trial', 'PictureSlide__RESP')])
mat_label <- merge(mat_label, dat_uniq_labl1, by = c('ID', 'Trial'), sort=FALSE)
dat_uniq_vas <- unique(dat[, c('ID', 'Trial', 'VASValue')])
mat_label <- merge(mat_label, dat_uniq_vas, by = c('ID', 'Trial'), sort=FALSE)
dat_uniq_gender_age <- unique(dat[, c('ID', 'Trial', 'Gender', 'Age')])
mat_label <- merge(mat_label, dat_uniq_gender_age, by = c('ID', 'Trial'), sort=FALSE)

tib_label <- as_tibble(mat_label)
#participants 56, 25, 26, 27 exclude
tib_label <- subset(tib_label, tib_label$ID != 25)
tib_label <- subset(tib_label, tib_label$ID != 26)
tib_label <- subset(tib_label, tib_label$ID != 27)
tib_label <- subset(tib_label, tib_label$ID != 56)
dataf <- as.data.frame(tib_label)

# Angry
for (i in 1:6592){
  if (dataf[i, 'label_string'] == 'angry'){
    dataf[i, 'y_angry'] = 1
  } else{
    dataf[i, 'y_angry'] = 0
  }
}

# Scared
for (i in 1:6592){
  if (dataf[i, 'label_string'] == 'scared'){
    dataf[i, 'y_scared'] = 1
  } else{
    dataf[i, 'y_scared'] = 0
  }
}

# Happy
for (i in 1:6592){
  if (dataf[i, 'label_string'] == 'happy'){
    dataf[i, 'y_happy'] = 1
  } else{
    dataf[i, 'y_happy'] = 0
  }
}

# Neutral
for (i in 1:6592){
  if (dataf[i, 'label_string'] == 'neutral'){
    dataf[i, 'y_neutral'] = 1
  } else{
    dataf[i, 'y_neutral'] = 0
  }
}

# Sad
for (i in 1:6592){
  if (dataf[i, 'label_string'] == 'sad'){
    dataf[i, 'y_sad'] = 1
  } else{
    dataf[i, 'y_sad'] = 0
  }
}


```


# Logistic regression

```{r}
# glm
data_glm <- glm(label_string ~ ., data = dataf,family = binomial)
summary(data_glm)

# multinom
library(nnet)
data_multinom <- multinom(label_string ~ ., data = dataf)
summary(data_multinom)

# p-values
z <- summary(data_multinom)$coefficients/summary(data_multinom)$standard.errors
p <- (1 - pnorm(abs(z), 0, 1)) * 2
p

# glmer
library(lme4)

# ANGRY
randomintercept <- glmer(y_angry ~ 
                           Gender + VASValue + Age + Trial
                         + Int_stim_Cor+Sl_stim_Cor+Int_bl_Cor+Sl_bl_Cor
                         + Int_stim_Zyg+Sl_stim_Zyg+Int_bl_Zyg+Sl_bl_Zyg
                         + Int_stim_SC+Sl_stim_SC+Int_bl_SC+Sl_bl_SC
                         + Int_stim_SKT+Sl_stim_SKT+Int_bl_SKT+Sl_bl_SKT
                         + Int_stim_DIA+Sl_stim_DIA+Int_bl_DIA+Sl_bl_DIA
                         + (1|ID), data = dataf, family = binomial,
                         nAGQ = 11, 
                      control=glmerControl(optimizer="bobyqa",optCtrl=list(
                        maxfun=2e4)))

#print(randomintercept, corr = FALSE)
summary(randomintercept)

randomslope.1 <- glmer(label_string ~ Int_stim_Cor+Sl_stim_Cor+Int_bl_Cor+Sl_bl_Cor
                         + Int_stim_Zyg+Sl_stim_Zyg+Int_bl_Zyg+Sl_bl_Zyg
                         + Int_stim_SC+Sl_stim_SC+Int_bl_SC+Sl_bl_SC
                         + Int_stim_SKT+Sl_stim_SKT+Int_bl_SKT+Sl_bl_SKT
                         + Int_stim_DIA+Sl_stim_DIA+Int_bl_DIA+Sl_bl_DIA
                         + (Int_stim_Cor|ID), data = dataf, family = binomial,
                         nAGQ = 1, control = 
                         glmerControl(optimizer ="bobyqa", optCtrl= list(
                           maxfun = 2e5
                         )))

summary(randomslope.1)

anova(randomintercept, randomslope.1) # not significant

randomslope.2 <- glmer(label_string ~ Int_stim_Cor+Sl_stim_Cor+Int_bl_Cor+Sl_bl_Cor
                         + Int_stim_Zyg+Sl_stim_Zyg+Int_bl_Zyg+Sl_bl_Zyg
                         + Int_stim_SC+Sl_stim_SC+Int_bl_SC+Sl_bl_SC
                         + Int_stim_SKT+Sl_stim_SKT+Int_bl_SKT+Sl_bl_SKT
                         + Int_stim_DIA+Sl_stim_DIA+Int_bl_DIA+Sl_bl_DIA
                         + (Sl_stim_Cor|ID), data = dataf, family = binomial,
                         nAGQ = 1, control = 
                         glmerControl(optimizer="bobyqa", optCtrl = list(
                           maxfun=2e5
                           )))

anova(randomintercept, randomslope.2) # not significant

randomslope.3 <- glmer(label_string ~ Int_stim_Cor+Sl_stim_Cor+Int_bl_Cor+Sl_bl_Cor
                         + Int_stim_Zyg+Sl_stim_Zyg+Int_bl_Zyg+Sl_bl_Zyg
                         + Int_stim_SC+Sl_stim_SC+Int_bl_SC+Sl_bl_SC
                         + Int_stim_SKT+Sl_stim_SKT+Int_bl_SKT+Sl_bl_SKT
                         + Int_stim_DIA+Sl_stim_DIA+Int_bl_DIA+Sl_bl_DIA
                         + (Int_bl_Cor|ID), data = dataf, family = binomial,
                         nAGQ = 1, control = 
                         glmerControl(optimizer="bobyqa", optCtrl = list(
                           maxfun=2e5
                         )))

anova(randomintercept, randomslope.3) # not significant

randomslope.4 <- glmer(label_string ~ Int_stim_Cor+Sl_stim_Cor+Int_bl_Cor+Sl_bl_Cor
                         + Int_stim_Zyg+Sl_stim_Zyg+Int_bl_Zyg+Sl_bl_Zyg
                         + Int_stim_SC+Sl_stim_SC+Int_bl_SC+Sl_bl_SC
                         + Int_stim_SKT+Sl_stim_SKT+Int_bl_SKT+Sl_bl_SKT
                         + Int_stim_DIA+Sl_stim_DIA+Int_bl_DIA+Sl_bl_DIA
                         + (Sl_bl_Cor|ID), data = dataf, family = binomial,
                         nAGQ = 1, control = 
                         glmerControl(optimizer="bobyqa", optCtrl = list(
                           maxfun = 2e5
                         )))

anova(randomintercept, randomslope.4) # not significant

randomslope.5 <- glmer(label_string ~ Int_stim_Cor+Sl_stim_Cor+Int_bl_Cor+Sl_bl_Cor
                         + Int_stim_Zyg+Sl_stim_Zyg+Int_bl_Zyg+Sl_bl_Zyg
                         + Int_stim_SC+Sl_stim_SC+Int_bl_SC+Sl_bl_SC
                         + Int_stim_SKT+Sl_stim_SKT+Int_bl_SKT+Sl_bl_SKT
                         + Int_stim_DIA+Sl_stim_DIA+Int_bl_DIA+Sl_bl_DIA
                         + (Int_stim_Zyg|ID), data = dataf, family = binomial,
                         nAGQ = 1, control = 
                         glmerControl(optimizer="bobyqa", optCtrl = list(
                           maxfun = 2e5
                         )))

anova(randomintercept, randomslope.5) # not significant

randomslope.6 <- glmer(label_string ~ Int_stim_Cor+Sl_stim_Cor+Int_bl_Cor+Sl_bl_Cor
                         + Int_stim_Zyg+Sl_stim_Zyg+Int_bl_Zyg+Sl_bl_Zyg
                         + Int_stim_SC+Sl_stim_SC+Int_bl_SC+Sl_bl_SC
                         + Int_stim_SKT+Sl_stim_SKT+Int_bl_SKT+Sl_bl_SKT
                         + Int_stim_DIA+Sl_stim_DIA+Int_bl_DIA+Sl_bl_DIA
                         + (Sl_stim_Zyg|ID), data = dataf, family = binomial,
                         nAGQ = 1, control = 
                         glmerControl(optimizer="bobyqa", optCtrl = list(
                           maxfun = 2e5
                         )))
#Model is nearly unidentifiable: large eigenvalue ratio
 #- Rescale variables?

anova(randomintercept, randomslope.6) # not significant

randomslope.7 <- glmer(label_string ~ Int_stim_Cor+Sl_stim_Cor+Int_bl_Cor+Sl_bl_Cor
                         + Int_stim_Zyg+Sl_stim_Zyg+Int_bl_Zyg+Sl_bl_Zyg
                         + Int_stim_SC+Sl_stim_SC+Int_bl_SC+Sl_bl_SC
                         + Int_stim_SKT+Sl_stim_SKT+Int_bl_SKT+Sl_bl_SKT
                         + Int_stim_DIA+Sl_stim_DIA+Int_bl_DIA+Sl_bl_DIA
                         + (Int_bl_Zyg|ID), data = dataf, family = binomial,
                         nAGQ = 1, control = 
                         glmerControl(optimizer="bobyqa", optCtrl = list(
                           maxfun = 2e5
                         )))

anova(randomintercept, randomslope.7) # not significant

randomslope.8 <- glmer(label_string ~ Int_stim_Cor+Sl_stim_Cor+Int_bl_Cor+Sl_bl_Cor
                         + Int_stim_Zyg+Sl_stim_Zyg+Int_bl_Zyg+Sl_bl_Zyg
                         + Int_stim_SC+Sl_stim_SC+Int_bl_SC+Sl_bl_SC
                         + Int_stim_SKT+Sl_stim_SKT+Int_bl_SKT+Sl_bl_SKT
                         + Int_stim_DIA+Sl_stim_DIA+Int_bl_DIA+Sl_bl_DIA
                         + (Sl_bl_Zyg|ID), data = dataf, family = binomial,
                         nAGQ = 1, control = 
                         glmerControl(optimizer="bobyqa", optCtrl = list(
                           maxfun = 2e5
                         )))

anova(randomintercept, randomslope.8) # not significant

randomslope.9 <- glmer(label_string ~ Int_stim_Cor+Sl_stim_Cor+Int_bl_Cor+Sl_bl_Cor
                         + Int_stim_Zyg+Sl_stim_Zyg+Int_bl_Zyg+Sl_bl_Zyg
                         + Int_stim_SC+Sl_stim_SC+Int_bl_SC+Sl_bl_SC
                         + Int_stim_SKT+Sl_stim_SKT+Int_bl_SKT+Sl_bl_SKT
                         + Int_stim_DIA+Sl_stim_DIA+Int_bl_DIA+Sl_bl_DIA
                         + (Int_stim_SC|ID), data = dataf, family = binomial,
                         nAGQ = 1, control = 
                         glmerControl(optimizer="bobyqa", optCtrl = list(
                           maxfun = 2e5
                         )))

anova(randomintercept, randomslope.9) # not significant (almost)

randomslope.10 <- glmer(label_string ~ Int_stim_Cor+Sl_stim_Cor+Int_bl_Cor+Sl_bl_Cor
                         + Int_stim_Zyg+Sl_stim_Zyg+Int_bl_Zyg+Sl_bl_Zyg
                         + Int_stim_SC+Sl_stim_SC+Int_bl_SC+Sl_bl_SC
                         + Int_stim_SKT+Sl_stim_SKT+Int_bl_SKT+Sl_bl_SKT
                         + Int_stim_DIA+Sl_stim_DIA+Int_bl_DIA+Sl_bl_DIA
                         + (Sl_stim_SC|ID), data = dataf, family = binomial,
                         nAGQ = 1, control = 
                          glmerControl(optimizer="bobyqa", optCtrl = list(
                            maxfun = 2e5
                          )))

anova(randomintercept, randomslope.10) # not significant

randomslope.11 <- glmer(label_string ~ Int_stim_Cor+Sl_stim_Cor+Int_bl_Cor+Sl_bl_Cor
                         + Int_stim_Zyg+Sl_stim_Zyg+Int_bl_Zyg+Sl_bl_Zyg
                         + Int_stim_SC+Sl_stim_SC+Int_bl_SC+Sl_bl_SC
                         + Int_stim_SKT+Sl_stim_SKT+Int_bl_SKT+Sl_bl_SKT
                         + Int_stim_DIA+Sl_stim_DIA+Int_bl_DIA+Sl_bl_DIA
                         + (Int_bl_SC|ID), data = dataf, family = binomial,
                         nAGQ = 1, control = 
                          glmerControl(optimizer="bobyqa", optCtrl = list(
                            maxfun = 2e5
                          )))

anova(randomintercept, randomslope.11) # not significant

randomslope.12 <- glmer(label_string ~ Int_stim_Cor+Sl_stim_Cor+Int_bl_Cor+Sl_bl_Cor
                         + Int_stim_Zyg+Sl_stim_Zyg+Int_bl_Zyg+Sl_bl_Zyg
                         + Int_stim_SC+Sl_stim_SC+Int_bl_SC+Sl_bl_SC
                         + Int_stim_SKT+Sl_stim_SKT+Int_bl_SKT+Sl_bl_SKT
                         + Int_stim_DIA+Sl_stim_DIA+Int_bl_DIA+Sl_bl_DIA
                         + (Sl_bl_SC|ID), data = dataf, family = binomial,
                         nAGQ = 1, control = 
                          glmerControl(optimizer="bobyqa", optCtrl = list(
                            maxfun = 2e5
                          )))

anova(randomintercept, randomslope.12) # not significant

randomslope.13 <- glmer(label_string ~ Int_stim_Cor+Sl_stim_Cor+Int_bl_Cor+Sl_bl_Cor
                         + Int_stim_Zyg+Sl_stim_Zyg+Int_bl_Zyg+Sl_bl_Zyg
                         + Int_stim_SC+Sl_stim_SC+Int_bl_SC+Sl_bl_SC
                         + Int_stim_SKT+Sl_stim_SKT+Int_bl_SKT+Sl_bl_SKT
                         + Int_stim_DIA+Sl_stim_DIA+Int_bl_DIA+Sl_bl_DIA
                         + (Int_stim_SKT|ID), data = dataf, family = binomial,
                         nAGQ = 1, control = 
                          glmerControl(optimizer="bobyqa", optCtrl = list(
                            maxfun = 2e5
                          )))

anova(randomintercept, randomslope.13) # not significant

randomslope.14 <- glmer(label_string ~ Int_stim_Cor+Sl_stim_Cor+Int_bl_Cor+Sl_bl_Cor
                         + Int_stim_Zyg+Sl_stim_Zyg+Int_bl_Zyg+Sl_bl_Zyg
                         + Int_stim_SC+Sl_stim_SC+Int_bl_SC+Sl_bl_SC
                         + Int_stim_SKT+Sl_stim_SKT+Int_bl_SKT+Sl_bl_SKT
                         + Int_stim_DIA+Sl_stim_DIA+Int_bl_DIA+Sl_bl_DIA
                         + (Sl_stim_SKT|ID), data = dataf, family = binomial,
                         nAGQ = 1, control = 
                          glmerControl(optimizer="bobyqa", optCtrl = list(
                            maxfun = 2e5
                          )))

anova(randomintercept, randomslope.14) # not significant

randomslope.15 <- glmer(label_string ~ Int_stim_Cor+Sl_stim_Cor+Int_bl_Cor+Sl_bl_Cor
                         + Int_stim_Zyg+Sl_stim_Zyg+Int_bl_Zyg+Sl_bl_Zyg
                         + Int_stim_SC+Sl_stim_SC+Int_bl_SC+Sl_bl_SC
                         + Int_stim_SKT+Sl_stim_SKT+Int_bl_SKT+Sl_bl_SKT
                         + Int_stim_DIA+Sl_stim_DIA+Int_bl_DIA+Sl_bl_DIA
                         + (Int_bl_SKT|ID), data = dataf, family = binomial,
                         nAGQ = 1, control = 
                          glmerControl(optimizer="bobyqa", optCtrl = list(
                            maxfun = 2e5
                          )))

anova(randomintercept, randomslope.15) # not significant

randomslope.16 <- glmer(label_string ~ Int_stim_Cor+Sl_stim_Cor+Int_bl_Cor+Sl_bl_Cor
                         + Int_stim_Zyg+Sl_stim_Zyg+Int_bl_Zyg+Sl_bl_Zyg
                         + Int_stim_SC+Sl_stim_SC+Int_bl_SC+Sl_bl_SC
                         + Int_stim_SKT+Sl_stim_SKT+Int_bl_SKT+Sl_bl_SKT
                         + Int_stim_DIA+Sl_stim_DIA+Int_bl_DIA+Sl_bl_DIA
                         + (Sl_bl_SKT|ID), data = dataf, family = binomial,
                         nAGQ = 1, control = 
                          glmerControl(optimizer="bobyqa", optCtrl = list(
                            maxfun = 2e5
                          )))

anova(randomintercept, randomslope.16) # not significant

randomslope.17 <- glmer(label_string ~ Int_stim_Cor+Sl_stim_Cor+Int_bl_Cor+Sl_bl_Cor
                         + Int_stim_Zyg+Sl_stim_Zyg+Int_bl_Zyg+Sl_bl_Zyg
                         + Int_stim_SC+Sl_stim_SC+Int_bl_SC+Sl_bl_SC
                         + Int_stim_SKT+Sl_stim_SKT+Int_bl_SKT+Sl_bl_SKT
                         + Int_stim_DIA+Sl_stim_DIA+Int_bl_DIA+Sl_bl_DIA
                         + (Int_stim_DIA|ID), data = dataf, family = binomial,
                         nAGQ = 1, control = 
                          glmerControl(optimizer="bobyqa", optCtrl = list(
                            maxfun = 2e5
                          )))

anova(randomintercept, randomslope.17) # not significant

randomslope.18 <- glmer(label_string ~ Int_stim_Cor+Sl_stim_Cor+Int_bl_Cor+Sl_bl_Cor
                         + Int_stim_Zyg+Sl_stim_Zyg+Int_bl_Zyg+Sl_bl_Zyg
                         + Int_stim_SC+Sl_stim_SC+Int_bl_SC+Sl_bl_SC
                         + Int_stim_SKT+Sl_stim_SKT+Int_bl_SKT+Sl_bl_SKT
                         + Int_stim_DIA+Sl_stim_DIA+Int_bl_DIA+Sl_bl_DIA
                         + (Sl_stim_DIA|ID), data = dataf, family = binomial,
                         nAGQ = 1, control = 
                          glmerControl(optimizer="bobyqa", optCtrl = list(
                            maxfun = 2e5
                          )))

anova(randomintercept, randomslope.18) # not significant

randomslope.19 <- glmer(label_string ~ Int_stim_Cor+Sl_stim_Cor+Int_bl_Cor+Sl_bl_Cor
                         + Int_stim_Zyg+Sl_stim_Zyg+Int_bl_Zyg+Sl_bl_Zyg
                         + Int_stim_SC+Sl_stim_SC+Int_bl_SC+Sl_bl_SC
                         + Int_stim_SKT+Sl_stim_SKT+Int_bl_SKT+Sl_bl_SKT
                         + Int_stim_DIA+Sl_stim_DIA+Int_bl_DIA+Sl_bl_DIA
                         + (Int_bl_DIA|ID), data = dataf, family = binomial,
                         nAGQ = 1, control = 
                          glmerControl(optimizer="bobyqa", optCtrl = list(
                            maxfun = 2e5
                          )))

anova(randomintercept, randomslope.19) # not

randomslope.20 <- glmer(label_string ~ Int_stim_Cor+Sl_stim_Cor+Int_bl_Cor+Sl_bl_Cor
                         + Int_stim_Zyg+Sl_stim_Zyg+Int_bl_Zyg+Sl_bl_Zyg
                         + Int_stim_SC+Sl_stim_SC+Int_bl_SC+Sl_bl_SC
                         + Int_stim_SKT+Sl_stim_SKT+Int_bl_SKT+Sl_bl_SKT
                         + Int_stim_DIA+Sl_stim_DIA+Int_bl_DIA+Sl_bl_DIA
                         + (Sl_bl_DIA|ID), data = dataf, family = binomial,
                         nAGQ = 1, control = 
                          glmerControl(optimizer="bobyqa", optCtrl = list(
                            maxfun = 2e5
                          )))

anova(randomintercept, randomslope.20) # not significant


library(GLMMadaptive)
class(data$PictureSlide__RESP)

mixed_randomint <- mixed_model(fixed = y_angry ~ Trial + Age + VASValue + Gender+ Int_stim_Cor+Sl_stim_Cor+Int_bl_Cor+Sl_bl_Cor
                         + Int_stim_Zyg+Sl_stim_Zyg+Int_bl_Zyg+Sl_bl_Zyg
                         + Int_stim_SC+Sl_stim_SC+Int_bl_SC+Sl_bl_SC
                         + Int_stim_SKT+Sl_stim_SKT+Int_bl_SKT+Sl_bl_SKT
                         + Int_stim_DIA+Sl_stim_DIA+Int_bl_DIA+Sl_bl_DIA,
            random = ~1|ID, 
            data = dataf, 
            family = binomial, 
            control = list(
              iter_EM = 0
            ))

summary(mixed_randomint)
mixed_randomint$

mixed_randomslop.1 <- mixed_model(fixed = label_string ~ Trial + Age + VASValue + Gender+ Int_stim_Cor+Sl_stim_Cor+Int_bl_Cor+Sl_bl_Cor
                         + Int_stim_Zyg+Sl_stim_Zyg+Int_bl_Zyg+Sl_bl_Zyg
                         + Int_stim_SC+Sl_stim_SC+Int_bl_SC+Sl_bl_SC
                         + Int_stim_SKT+Sl_stim_SKT+Int_bl_SKT+Sl_bl_SKT
                         + Int_stim_DIA+Sl_stim_DIA+Int_bl_DIA+Sl_bl_DIA,
            random = ~Int_stim_Cor|ID, 
            data = dataf, 
            family = binomial, 
            control = list(
              iter_EM = 0
            ))

anova(mixed_randomint, mixed_randomslop.1)

mixed_randomslop.2 <- mixed_model(fixed = label_string ~ Int_stim_Cor+Sl_stim_Cor+Int_bl_Cor+Sl_bl_Cor
                         + Int_stim_Zyg+Sl_stim_Zyg+Int_bl_Zyg+Sl_bl_Zyg
                         + Int_stim_SC+Sl_stim_SC+Int_bl_SC+Sl_bl_SC
                         + Int_stim_SKT+Sl_stim_SKT+Int_bl_SKT+Sl_bl_SKT
                         + Int_stim_DIA+Sl_stim_DIA+Int_bl_DIA+Sl_bl_DIA,
            random = ~Sl_stim_Cor|ID, 
            data = dataf, 
            family = binomial)

anova(mixed_randomint, mixed_randomslop.2)

mixed_randomslop.3 <- mixed_model(fixed = label_string ~ Int_stim_Cor+Sl_stim_Cor+Int_bl_Cor+Sl_bl_Cor
                         + Int_stim_Zyg+Sl_stim_Zyg+Int_bl_Zyg+Sl_bl_Zyg
                         + Int_stim_SC+Sl_stim_SC+Int_bl_SC+Sl_bl_SC
                         + Int_stim_SKT+Sl_stim_SKT+Int_bl_SKT+Sl_bl_SKT
                         + Int_stim_DIA+Sl_stim_DIA+Int_bl_DIA+Sl_bl_DIA,
            random = ~Int_bl_Cor|ID, 
            data = dataf, 
            family = binomial)

anova(mixed_randomint, mixed_randomslop.3)

mixed_randomslop.4 <- mixed_model(fixed = label_string ~ Int_stim_Cor+Sl_stim_Cor+Int_bl_Cor+Sl_bl_Cor
                         + Int_stim_Zyg+Sl_stim_Zyg+Int_bl_Zyg+Sl_bl_Zyg
                         + Int_stim_SC+Sl_stim_SC+Int_bl_SC+Sl_bl_SC
                         + Int_stim_SKT+Sl_stim_SKT+Int_bl_SKT+Sl_bl_SKT
                         + Int_stim_DIA+Sl_stim_DIA+Int_bl_DIA+Sl_bl_DIA,
            random = ~Sl_bl_Cor|ID, 
            data = dataf, 
            family = binomial)

anova(mixed_randomint, mixed_randomslop.4)

mixed_randomslop.5 <- mixed_model(fixed = label_string ~ Int_stim_Cor+Sl_stim_Cor+Int_bl_Cor+Sl_bl_Cor
                         + Int_stim_Zyg+Sl_stim_Zyg+Int_bl_Zyg+Sl_bl_Zyg
                         + Int_stim_SC+Sl_stim_SC+Int_bl_SC+Sl_bl_SC
                         + Int_stim_SKT+Sl_stim_SKT+Int_bl_SKT+Sl_bl_SKT
                         + Int_stim_DIA+Sl_stim_DIA+Int_bl_DIA+Sl_bl_DIA,
            random = ~Int_stim_Zyg|ID, 
            data = dataf, 
            family = binomial)

anova(mixed_randomint, mixed_randomslop.5)

mixed_randomslop.6 <- mixed_model(fixed = label_string ~ Int_stim_Cor+Sl_stim_Cor+Int_bl_Cor+Sl_bl_Cor
                         + Int_stim_Zyg+Sl_stim_Zyg+Int_bl_Zyg+Sl_bl_Zyg
                         + Int_stim_SC+Sl_stim_SC+Int_bl_SC+Sl_bl_SC
                         + Int_stim_SKT+Sl_stim_SKT+Int_bl_SKT+Sl_bl_SKT
                         + Int_stim_DIA+Sl_stim_DIA+Int_bl_DIA+Sl_bl_DIA,
            random = ~Sl_stim_Zyg|ID, 
            data = dataf, 
            family = binomial)

anova(mixed_randomint, mixed_randomslop.6)

mixed_randomslop.7 <- mixed_model(fixed = label_string ~ Int_stim_Cor+Sl_stim_Cor+Int_bl_Cor+Sl_bl_Cor
                         + Int_stim_Zyg+Sl_stim_Zyg+Int_bl_Zyg+Sl_bl_Zyg
                         + Int_stim_SC+Sl_stim_SC+Int_bl_SC+Sl_bl_SC
                         + Int_stim_SKT+Sl_stim_SKT+Int_bl_SKT+Sl_bl_SKT
                         + Int_stim_DIA+Sl_stim_DIA+Int_bl_DIA+Sl_bl_DIA,
            random = ~Int_bl_Zyg|ID, 
            data = dataf, 
            family = binomial)

anova(mixed_randomint, mixed_randomslop.7)

mixed_randomslop.8 <- mixed_model(fixed = label_string ~ Int_stim_Cor+Sl_stim_Cor+Int_bl_Cor+Sl_bl_Cor
                         + Int_stim_Zyg+Sl_stim_Zyg+Int_bl_Zyg+Sl_bl_Zyg
                         + Int_stim_SC+Sl_stim_SC+Int_bl_SC+Sl_bl_SC
                         + Int_stim_SKT+Sl_stim_SKT+Int_bl_SKT+Sl_bl_SKT
                         + Int_stim_DIA+Sl_stim_DIA+Int_bl_DIA+Sl_bl_DIA,
            random = ~Sl_bl_Zyg|ID, 
            data = dataf, 
            family = binomial)

anova(mixed_randomint, mixed_randomslop.8)

mixed_randomslop.9 <- mixed_model(fixed = label_string ~ Int_stim_Cor+Sl_stim_Cor+Int_bl_Cor+Sl_bl_Cor
                         + Int_stim_Zyg+Sl_stim_Zyg+Int_bl_Zyg+Sl_bl_Zyg
                         + Int_stim_SC+Sl_stim_SC+Int_bl_SC+Sl_bl_SC
                         + Int_stim_SKT+Sl_stim_SKT+Int_bl_SKT+Sl_bl_SKT
                         + Int_stim_DIA+Sl_stim_DIA+Int_bl_DIA+Sl_bl_DIA,
            random = ~Int_stim_SC|ID, 
            data = dataf, 
            family = binomial)

anova(mixed_randomint, mixed_randomslop.9)

mixed_randomslop.10 <- mixed_model(fixed = label_string ~ Int_stim_Cor+Sl_stim_Cor+Int_bl_Cor+Sl_bl_Cor
                         + Int_stim_Zyg+Sl_stim_Zyg+Int_bl_Zyg+Sl_bl_Zyg
                         + Int_stim_SC+Sl_stim_SC+Int_bl_SC+Sl_bl_SC
                         + Int_stim_SKT+Sl_stim_SKT+Int_bl_SKT+Sl_bl_SKT
                         + Int_stim_DIA+Sl_stim_DIA+Int_bl_DIA+Sl_bl_DIA,
            random = ~Sl_stim_SC|ID, 
            data = dataf, 
            family = binomial)

anova(mixed_randomint, mixed_randomslop.10)

mixed_randomslop.11 <- mixed_model(fixed = label_string ~ Trial+ Int_stim_Cor+Sl_stim_Cor+Int_bl_Cor+Sl_bl_Cor
                         + Int_stim_Zyg+Sl_stim_Zyg+Int_bl_Zyg+Sl_bl_Zyg
                         + Int_stim_SC+Sl_stim_SC+Int_bl_SC+Sl_bl_SC
                         + Int_stim_SKT+Sl_stim_SKT+Int_bl_SKT+Sl_bl_SKT
                         + Int_stim_DIA+Sl_stim_DIA+Int_bl_DIA+Sl_bl_DIA,
            random = ~Int_bl_SC|ID, 
            data = dataf, 
            family = binomial)
summary(mixed_randomslop.11)
anova(mixed_randomint, mixed_randomslop.11)




  
length(getME(randomslope.1,"theta"))
length(fixef(randomslope.1))

tt <- getME(randomslope.3,"theta")
ll <- getME(randomslope.3,"lower")
min(tt[ll==0])

isSingular(randomslope.5)
tt <- getME(randomslope.5,"theta")
ll <- getME(randomslope.5,"lower")
min(tt[ll==0])
isSingular(randomslope.5, tol = 1e-400)
#check.conv.singular = .makeCC(action = "message",  tol = 1e-400)
#age, gender, vas
dataf$label_string

```

